Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Remove note on Kraken in 6.1 to avoid repeating section 4

\subsection{Training and evaluation protocol}
Only CmBERT and CmBERT+ptrn are considered since experiment 1 shows that SpaCy NER is systematically outperformed by these two models.

>>>>

\subsection{Training and evaluation protocol}
Only CmBERT and CmBERT+ptrn are considered since the first experiment shows that SpaCy NER is outperformed by these two models for all sizes of training sets.
